Decades of ``group polarization'' replications may be undermined by high false discovery rates

### 2024-12-06 GroupPolarizationStatmod/paper/ms.tex
final draft of plots before sending to p

\subsection{Ninety percent of detections are plausibly false}

@@

>>>>

\subsection{Ninety percent of detections identified as plausibly false}

@@

\begin{figure}
  \caption{\textbf{Significance value, $d^*$, to limit family-wise error 
  rate of 0.05 for each identified study.} \mt{Does this make sense? Order by the
rankings in fdr\_vs\_experiment plots to better understand/compare.}}
  \centering
    \includegraphics[width=0.55\textwidth]{Figures/sigval_for_low_fwer.pdf}
  \label{fig:sigval_for_low_fwer}
\end{figure}
